MSD panels 1, 2 and 3 Explant Supernatant

### 2016-09-22 MSD_panels_1_2_3_explant_sup_analysis.Rmd
knit for github

ggplot(merge24And3, aes(x = Donor, y = Assay))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus, scales = "free_x")+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
```
This is just donors 317,318,323 and 324, which were interesting in the microarray

>>>>

ggplot(merge24And3, aes(x = Donor, y = Assay))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus, scales = "free_x")+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
```
